Modelling and Analysis of an Elevator System with NuSMV2

### 2013-06-07 paper/main.tex
paper: finalized substantive information

	% Baier & katoen 5.5
	% LTL

@@

	\subsection{Model with strategy}
	We think that these fairness constraints are somewhat questionable. A desired property should follow from the system specifications and should not be explicitly be part of those specifications. This is why we have a third model (\texttt{elevator\_simple\_smart.smv}) in which we implement a simple elevator strategy. The lowest higher floor is now preferred. If there are no requests on higher floors, the lowest requested floor is chosen as the next target. We can confirm that this simple strategy also excludes any unwanted behaviour.

@@

@@

	\begin{figure}[H]
		\begin{center}
			\begin{tabular}{r|r|r}
				\backslashbox{$F$}{$n$} & simple & smart \\ \hline
				2	& 0.028		& 0.025		\\ \hline
				3	& 0.030		& 0.027		\\ \hline
				4	& 0.034		& 0.045		\\ \hline
				5	& 0.040		& 0.058		\\ \hline
				6	& 0.051		& 0.092		\\ \hline 
				7	& 0.059		& 0.126		\\ \hline
				8	& 0.068		& 0.177		\\ \hline
				9	& 0.077		& 0.241		\\ \hline
				10	& 0.090		& 0.335		\\ \hline
				20	& 0.285		& 6.732		\\ \hline
				30	& 0.630		& 47.327	\\ \hline
				40	& 1.214		&		\\ \hline
				50	& 1.876		&		\\ \hline
				100	& 8.821		&		\\ \hline
			\end{tabular}
		\end{center}

@@

@@

@@

	\begin{figure}[H]
		\begin{center}
			\begin{tabular}{r|r|r}
				\backslashbox{$F$}{$n$} & simple & smart \\ \hline
				2	& 0.019		& 0.026		\\ \hline
				3	& 0.028		& 0.026		\\ \hline
				4	& 0.032		& 0.046		\\ \hline
				5	& 0.043		& 0.056		\\ \hline
				6	& 0.049		& 0.088		\\ \hline 
				7	& 0.065		& 0.136		\\ \hline
				8	& 0.067		& 0.191		\\ \hline
				9	& 0.083		& 0.263		\\ \hline
				10	& 0.098		& 0.363		\\ \hline
				20	& 0.279		& 4.138		\\ \hline
				30	& 0.722		& 20.980	\\ \hline
				40	& 1.203		& 71.612	\\ \hline
				50	& 1.920		&		\\ \hline
				100	& 9.267		&		\\ \hline
			\end{tabular}
		\end{center}

>>>>

	In this elaboration of the exercise on NuSMV2 for the Radboud University Nijmegen course ``Analysis of Embedded Systems'' we enumerate our notes and solutions for each problem. Besides this elaboration we have submitted the generated models and templates for these models by e-mail. For problem 4 and 5 we've written an application that measures the executiontime for a specific model in NuSMV. The sources for this application, this report and the models can be found on Github at \url{http://github.com/Wassasin/elevatormodel}.

@@

	\subsection{Model with strategy}
	We think that these fairness constraints are somewhat questionable. A desired property should follow from the system specifications and should not be explicitly be part of those specifications. This is why we have a third model (\texttt{elevator\_simple\_smart.smv}) in which we implement a specific simple elevator strategy: the lowest higher floor is now preferred. If there are no requests on higher floors, the lowest requested floor is chosen as the next target. We can confirm that this simple strategy also excludes any unwanted behaviour.

@@

	For this analysis we wrote a tool that generates a model for a specific number of floor and users, and measures the executiontime of that model in NuSMV2. If the modelchecker runs for more than 2 minutes, the attempt is terminated. Below we enumerate the executiontime in seconds for each instance of a model.

	Note that this tool also measures the time needed to fork it's process and to start and handle the termination of the NuSMV-process and that the execution of the NuSMV2-process may be pre-empted by the Operating System. Also note that each configuration is only tested once. Thus for models that do not need a lot of time to check (about 100 milliseconds or less), these measurements are not very accurate.

@@

	\begin{figure}[H]
		\begin{center}
			\begin{tabular}{r|r|r}
				\backslashbox{$F$}{$n$} & simple & simple\_smart \\ \hline
				2	& 0.028		& 0.025		\\ \hline
				3	& 0.030		& 0.027		\\ \hline
				4	& 0.034		& 0.045		\\ \hline
				5	& 0.040		& 0.058		\\ \hline
				6	& 0.051		& 0.092		\\ \hline 
				7	& 0.059		& 0.126		\\ \hline
				8	& 0.068		& 0.177		\\ \hline
				9	& 0.077		& 0.241		\\ \hline
				10	& 0.090		& 0.335		\\ \hline
				20	& 0.285		& 6.732		\\ \hline
				30	& 0.630		& 47.327	\\ \hline
				40	& 1.214		&		\\ \hline
				50	& 1.876		&		\\ \hline
				100	& 8.821		&		\\ \hline
			\end{tabular}
		\end{center}

@@

	Thus for the realistic model, with 2 users only 3 floors can be checked within 2 minutes. For the simple model, the elevator with more than 100 floors can be checked in the same time. The \texttt{simple\_smart} model can be checked for 30 floors.

@@

	To illustrate this, we have repeated the measurements we've one for Problem 4, but with the \texttt{-t} option on an empty file. We have summarized the results below:

@@

	\begin{figure}[H]
		\begin{center}
			\begin{tabular}{r|r|r}
				\backslashbox{$F$}{$n$} & simple & simple\_smart \\ \hline
				2	& 0.019		& 0.026		\\ \hline
				3	& 0.028		& 0.026		\\ \hline
				4	& 0.032		& 0.046		\\ \hline
				5	& 0.043		& 0.056		\\ \hline
				6	& 0.049		& 0.088		\\ \hline 
				7	& 0.065		& 0.136		\\ \hline
				8	& 0.067		& 0.191		\\ \hline
				9	& 0.083		& 0.263		\\ \hline
				10	& 0.098		& 0.363		\\ \hline
				20	& 0.279		& 4.138		\\ \hline
				30	& 0.722		& 20.980	\\ \hline
				40	& 1.203		& 71.612	\\ \hline
				50	& 1.920		&		\\ \hline
				100	& 9.267		&		\\ \hline
			\end{tabular}
		\end{center}
